Modified replication

### 2020-06-05 rep_nosmooth/README.Rmd
add note checking RNG seed variance
How much does AUC-ROC vary between model runs when you don't see RNG seeds? Generally much less than 0.01. This is with the base spec escalation model, anecdotally, some of the other models, especially in Table 2, can vary more.

In order to be able to run the models needed to create tables 1 and 2 more quickly than with the original replication code, the code here has been refactored to enable running in parallel. Here is a summary of the major changes:

- `re-save-data.R` changes the format of the saved 1-month and 6-month data versions from Stata 13 .dta files to R .rds format. This can be read much quicker than the Stata format. 
- `setup-model-table.R` encodes all the various pieces of information needed to actually run the models reflected in tables 1 and 2. In the original replication files this is done in bits and pieces in `+master.R`, `code/[1|6]mo_define_models.R`, and each model runner file, e.g. `code/1mo_run_escalation.R`. The primary output are several files written to the `output/model-definitions` folder. More details on this below.
- `model-runner.R` runs the models. Adjust the number of WORKERS at the top of the script as needed based on the number of cores on your computer. The primary output of this script is `output/model-table-w-results.csv`
- `recreate-tables.R` recreates the original and non-smooth ROC versions of Tables 1 and 2.

@@

## Table 1

### Original, smoothed ROC curves

```{r}
table1_smooth <- read_csv("output/table1-smooth.csv")

table1_smooth %>%
  knitr::kable(digits = 2,
               caption = "Alternative Table 1 with non-smoothed AUC-ROC")
```

### With conventional ROC curves

```{r}
table1_nosmooth <- read_csv("output/table1-nosmooth.csv")
table1_nosmooth %>%
  knitr::kable(digits = 2,
               caption = "Alternative Table 1 with non-smoothed AUC-ROC")
```

>>>>

In order to be able to run the models needed to create tables 1 and 2 more quickly than with the original replication code, the code here has been re-factored to enable running in parallel. Here is a summary of the major changes:

- `re-save-data.R` changes the format of the saved 1-month and 6-month data versions from Stata 13 .dta files to R .rds format. This can be read much quicker than the Stata format. 
- `setup-model-table.R` encodes all the various pieces of information needed to actually run the models reflected in tables 1 and 2. In the original replication files this is done in bits and pieces in `+master.R`, `code/[1|6]mo_define_models.R`, and each model runner file, e.g. `code/1mo_run_escalation.R`. The primary output are several files written to the `output/model-definitions` folder. More details on this below.
- `model-runner.R` runs the models. Adjust the number of WORKERS at the top of the script as needed based on the number of cores on your computer. The primary output of this script is `output/model-table-w-results.csv` and `output/all-predictions.R`.
- `recreate-tables.R` recreates the original and non-smooth ROC versions of Tables 1 and 2 using `output/model-table-w-results.csv` and `output/all-predictions.R`.

In addition, there are some ancillary materials.

- [variance.md](/variance.md) examines how much the AUC-ROC results vary when you don't set an RNG seed. For the base specification escalation model, the variance is significantly below 0.01, and small changes in the Table 1 and 2 replications mainly occur when the distribution straddles a threshold used for rounding, e.g. 0.825. 
- `make-original-tables.R` is a by-hand coding of the values reported for Tables 1, 2, and 4 in B&S 2020.

@@
